\chapter{Conclusions}
In this thesis, a system for position-based data acquisition was designed. This system consists of a hardware transducer module that can easily be build based on the Arduino platform and an Android application. The hardware transducer can easily be interfaced to a multitude of sensors. In order to demonstrate the capabilities of the system a transducer device containing an air humidity, an air temperature and an encapsulated temperature sensor which might, for example, be used to measure water and soil temperatures, has been build. The system contains the capability to export data to other Android apps including cloud storage providers. 

In a system field test, the system has been proven to be able to successfully collect water and air temperature data at different waterbodies around the university of Bremen. The data from the field test has been exported to a comma separated values file which was imported and visualized in Microsoft Excel and Matlab.

A transducer device for the system can be build using an Arduino microcontroller board, a Bluetooth module, a power source and the desired sensors. The embedded software developed in this thesis is easily adaptable to use various types of sensors including but not limited to sensors providing I$^2$C, SPI, analog and UART output. When the transducer device has been built successfully, a single button press on either the transducer device or in the application user interface triggers a measurement.

As the communication protocol is fully documented, potentially a transducer device interfacing the Android app could be built from other microcontroller platforms as long as they can send correctly formatted data through a Bluetooth RFCOMM channel.

The Android application software offers a user interface following the material design introduced in Android 5.0 Lollipop but still remains compatible back to Android 2.3 Gingerbread. The software offers a visualization of the recorded data in a list and on a map (leveraging map data provided by Google maps). Data records can be deleted individually or giving a threshold for the datasets age. The data visualization can be filtered and sorted by the receive time.

Data stored in the app can be exported to a comma separated values (\texttt{.csv}) file. The decimal mark and the cell separator used in the exported file can be adjusted to suit the requirements of the software the data should be imported into. Data exported can be analyzed and visualized using most data analysis software including but not limited to Microsoft Excel and Matlab. 